---
title: "Tuning"
output: html_document
---

~~~{=comment}
This report created spring 2026
It shows a scatter plot of two performance metrics with points for each
model in the grid search and density plots showing the distribution 
of a number of performance metrics.

It relies on plot_tuning(), plot_gridsearch_metrics(), format_metrics(),
identify_best_model, tuning_n_best, tuning_best_colors, and tuning_symbology 
defined in BirdFlowPipeline.

If you edit this doc you should re-install the package. Load all may not be enough.
~~~


```{r setup tuning, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# This document exists to provide an optional section in the species reports
# on model tuning.

if(!exists("train_metrics") | !exists("bf") | !exists("test_metrics"))  
  stop("Parent document should define bf, test_metrics, and train_metrics")

if (!all(c("cor_threshold", "cor_metric") %in% names(p)) && !is.na(p$cor_threshold) & !is.na(p$cor_metric))
  stop("Parent document should define cor_metric and cor_threshold")

cor_threshold <- p$cor_threshold
cor_metric <- p$cor_metric

hp <- bf$metadata$hyperparameters


```


## Model Tuning

### Selected hyper parameters

```{r selection_criteria, results='asis', echo = FALSE}
if(!is.na(selection_criteria))
  cat("Selection criteria: ", selection_criteria, "  \n")
```
Distance weight: `r hp$dist_weight`  
Entropy weight: `r hp$ent_weight`  
Observation weight: `r hp$obs_weight`  
Distance power: `r hp$dist_pow`  

### Performance metric trade offs 


```{r tuning plot, echo = FALSE}

plot_tuning(train = train_metrics, test = test_metrics, bf = bf, use = "train", cor_threshold = cor_threshold, cor_metric = cor_metric)

```

The candidate and best models plotted against two possible selection criteria:
log likelihood and relative distance gain.

### Candidate model performance for other metrics

The distribution of each metric across grid search runs where the 
distribution correlation was above `r cor_threshold`.  The metric values for this model,
the best log likelihood, and the best distance gained model are shown as 
vertical lines.  Each x axis represents values for the metric while the 
y axis is the density of values across the grid search results
which represented the training S&T Distributions with high fidelity 
(`r cor_metric`  above `r cor_threshold`).

```{r metrics, echo = FALSE, fig.height= 10}
plot_grid_search_metrics(train_metrics = train_metrics, test_metrics = test_metrics, bf = bf, cor_threshold = cor_threshold, cor_metric = cor_metric, include = included_metrics)
```


